Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-09-12 draft/response_to_referee.txt

Following the suggestion by the referee, we now try to explain this better in Section 2.2, 
Section 3.1, and Section 3.2.3.

-----
# 3.  Missing Definitions

The referee is correct that some of these basic definitions should be explained better.  
Most of these concepts are explained and discussed in great details in the hscPipe paper (Bosch et al. 2017)
and the Data Release 1 Paper (Aihara et al. 2017).  We emphasize the basic definitions of these values at the
end of the introduction section and point the authors to the Bosch+2017 paper for more details.

<1> HSC pipeline performs multi-step photometric calibrations against the Pan-STARRS system, hence all the
fluxes and magnitudes measured by hscPipe are already calibrated into the AB magnitude system.  Therefore, the
pixel values on the calibrated single-Visit and coadd images can be directly related to fluxes in physical
unit, and can be converted into magnitudes using a simple calibration zeropoint (27.0).  Users of HSC survey
data should not worry that the definition of magnitude is affected by filter or exposure time.
Through out this work, we assume that all magnitudes of synthetic objects are also in AB system, and they are 
converted into fluxes using the same zeropoint.

<2> The CCD processing provides us calibrated exposures that include both the detrended, background-subtracted
image and an image containing per-pixel estimate of the variance. The following coaddition process also takes
the variance information into account, uses the inverse of the mean variance of the input images to set the
weights for coaddition, and calculates the per-pixel variance for the coadd images. Both the PSF and CModel
photometry take these variance images into account, and provide meaningful estimations of flux error for the
coadd images.  
    - The HSC pipeline uses matched-filter method to estimate the PSF fluxes.  Per-pixel variance information
      is taken into account when estimating the flux error.  Please see Section 4.9.5 of Bosch+2017 for more
      technical details.  
    - The HSC CModel photometry is modified and improved based on the SDSS version.  It fits linear
      combination of two basic parametric models to the 2-D flux distribution of galaxy after taking PSF
      convolution into account.  It has the advantage of providing consistent multiband photometry for
      extended objects and having reliable performance for very faint object. 
      Please see Section 4.9.9 and Appendix 2 of Bosch+2017 for technical details of the CModel algorithm. 
    - For CModel photometry, it is optional to use per-pixel inverse square root of the variance information
      as weights during the fitting (when usePixelWeights=True).  By default, usePixelWeights=False, and a
      constant weight is used for an object.  Again we will refer the reader to Bosch+2017 for more details
      about this.

<3> We understand the referee's concern, and it is true that based on statistics of photons, we could have
more clear definition of signal-to-noise ratio (S/N).  However, in practice, it is not realistic to use "photon
number" for statistics or separately account for the noise from readout, dark, and sky background.  Each CCD
on the camira has four amplifiers that have slightly different effective gain; individual CCD images need to
be detrended, calibrated, and background subtracted before coaddition; single exposures with different seeings
are warped before they are coadded into a final image using appropriate weighting.  All these processes make
it difficult to trace back to the origianl photon statistics.  For instance, on the coadd image, there are
covariances between adjacent pixels due to the warping process.  On the other hand, hscPipe calibrates the
pixels values on both coadd and single-Visit images to physically meaningful flux scale, and provides
correponding variance information that reflect the per-pixel uncertainties after all these complex reduction
steps.  Based on this design, scientific user of HSC data can use the flux value and its uncertainty from
hscPipe to estimate the S/N of the object under certain photometric method.  
    - Throughout this work, S/N is defined as the ration between a flux measurement and its uncertainty (flux
      / flux_err).  Same definition is adopted by both Bosch+2017 (hscPipe paper) and Aihara+2017 (HSC DR1
      paper), along with a series of science papers.  
    - Under this definition, 5 sigma detection corresponds to a S/N=5 flux measurement under certain
      photometric method.  The same concept is adopted by both Bosch+2017 (hscPipe paper) and Aihara+2017 
      (HSC DR1 paper), along with a series of science papers. 
    - Both the PSF and CModel photometry algorithms convolve a model for the true object’s morphology with 
      the effective PSF model at the position of the object, which maximizes S/N (see Bosch+2017)

The changes of text related to this comment are: 
    - At the end of Introduction section, we make it clear that we are using AB system, and explain the
      definiton of S/N and Nxsigma detection.  
    - At the end of Section 2.2, we provide more details related to the flux measurements for PSF and CModel
      photometry.  We also refer the reader to Bosch+2017 for more technical details. 
    - Section 6.4: slightly more details about the usePixelWeights option and reference to hscPipe paper.

-----
# 4. CModel algorithm

We agree with the referee that the details of CModel algorithm should be explained better.  However, limited
by the scope of this work, we can not afford to show all the technical details.  As mentioned, we expanded

### 2017-09-12 draft/ms_v5.tex
Comment 2 3

%% ------------------------------------------------------------------------------------ %%
% Packages
\usepackage{url}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{multirow}

%% ------------------------------------------------------------------------------------ %%

@@

    The code for \synpipe{}, along with documentation and examples, is made available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of 
            photometric measurements (see \citealt{HSCDR1} for details). 
            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
            \cmodel{} photometry. 
            The \texttt{psf} photometry should provide the most appropriate magnitudes 
            and colors for point sources, while the \cmodel{} should be used for 
            galaxies.

@@

                \item \hscpipe{} uses matched-filter method to derive PSF magnitude 
                    with the centroid fixed. 
                    The algorithm matches the image of a star with the PSF model 
                    multiplied by an amplitude. 
                    This amplitude parameter is estimated via the inner product of 
                    the image and PSF model after shifting the model to the centroid 
                    of the star, then divide by the effective area of the PSF model.

                \item The HSC \cmodel{} algorithm is described in Bosch\etal (in prep), 
                    and is based on the version for the SDSS \cmodel{} magnitude 
                    (\citealt{Lupton2001, Abazajian2004}). 
                    It fits objects using both a de~Vaucouleurs and an exponential 
                    profiles convolved with the PSF model.  
                    \cmodel{} then linearly combines the two results to find the best 
                    fit to the galaxy image. 
                    \cmodel{} magnitudes are designed to yield accurate fluxes and 
                    colors for galaxies. 
                    Star--galaxy classification is also performed based on the 
                    difference between \texttt{psf} and \cmodel{}{} magnitudes.

@@

    Using our \synpipe{} tests, we discovered that the bug related to the priors only 
    presents when \texttt{usePixelWeight} configuration is set to \texttt{False} during 
    the data reduction. 
    The parameter controls whether or not the per-pixel variance information is used 
    during the model fitting process.  
    As one can see, this leads to significantly overestimated axis ratios for almost
    all galaxies\footnote{It also leads to underestimated half-light radius for the same
    galaxies.}.
    We repeat the \synpipe{} run for galaxies with 
    \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
    the problem. 
    When we use \texttt{usePixelWeight}$=$\texttt{True},
    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ provides an unbiased axis ratio 
    estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
    This change is still related to the bug in priors.  
    The actual effect of using per-pixel variance should be very small.  
    The next version of \hscpipe{} will fix this bug, and \synpipe{} will help evaluate 
    the precisions of shape and size measurements. 
    This is a good example that demonstrates how the \synpipe{} framework is valuable  
    for quality control and that can be used to improve \hscpipe{}.

    For the current HSC data release, we warn users against using the sizes and shapes 
    from \cmodel{} to study the structural properties of galaxies.

@@

@@

>>>>

%% ------------------------------------------------------------------------------------ %%
% Packages
\usepackage{url}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{multirow}

@@

    \song{
    Throughout this work, all magnitudes are in AB system (\citealt{Oke1974}). 
    Signal--to--noise ratio (\s2n{}) is defined as the ratio between a flux measurement 
    using certain algorithm (e.g. PSF, \cmodel{}) and its corresponding flux uncertainty 
    from \hscpipe{} ($\mathrm{Flux}/\sigma(\mathrm{Flux})$).  
    At the same time, a $5\sigma$ detection is equivalent to a flux measurement with 
    \s2n{}$=5$ using certain algorithm.  
    Such definitions are adopted in other works using HSC SSP data 
    (e.g. \citealt{Bosch2017, HSCDR1}).
    } 
    The code for \synpipe{}, along with documentation and examples, is made available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of 
            photometric measurements (see \citealt{HSCDR1} for details). 
            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
            \cmodel{} photometry. 
            \song{
            Both the \psf{} and \cmodel{} photometry algorithms take the PSF convolution 
            effect into account, and hence can provide consistent \forced{} photometry 
            across all bands and maximizes \s2n{}.  
            Although their accuracies depend on the accuracy of the PSF model and 
            the applicability of the adopted models, they still provide the most useful 
            flux information for stars and galaxies, especially for objects with 
            low-\s2n{}. 
            Please see Section~4 and Appendix~2 of \citet{Bosch2017} for detailed 
            descriptions of these algorithms.  
            }

@@

                \item \song{
                    Details of the HSC \psf{} photometry can be found in 
                    Section~4.9.5 of \citet{Bosch2017}. 
                    In short, 
                    }
                    \hscpipe{} uses matched-filter method to derive PSF magnitude 
                    with the centroid fixed. 
                    The algorithm matches the image of a star with the PSF model 
                    multiplied by an amplitude. 
                    This amplitude parameter is estimated via the inner product of 
                    the image and PSF model after shifting the model to the centroid 
                    of the star, then divide by the effective area of the PSF model.
                    \song{
                    It considers the per-pixel variance information when estimating 
                    the flux error. 
                    Flux uncertainty due to the uncertainty of centroid is ignored 
                    since it is subdominant even when \s2n{} is low. 
                    }

                \item \song{
                    Details about the HSC \cmodel{} photometry can be found in 
                    Section~4.9.9 and Appendix~2 of \citet{Bosch2017}. 
                    }
                    It is based on the version for the SDSS \cmodel{} magnitude 
                    (\citealt{Lupton2001, Abazajian2004}). 
                    \song{
                    It fits an object using both elliptical model with an exponential 
                    profile and de~Vaucouleurs profile with free amplitudes and shapes. 
                    Then it fits a linear combination of both models to the image while 
                    only allowing the amplitude of each component to change.  
                    The last step provides the \cmodel{} flux and flux error used in 
                    this work. 
                    This \cmodel{} flux can be roughly seen as the linear interpolation 
                    between exponential and de~Vaucouleurs models. 
                    Although these models are often not the most appropriate models for 
                    real galaxies, this method is shown to be robust and efficient, 
                    especially for poorly--resolved and/or low \s2n{} galaxies. 
                    }
                    Star--galaxy classification now is also performed based on the 
                    difference between \texttt{psf} and \cmodel{}{} magnitudes.

@@

    Using our \synpipe{} tests, we discovered that the bug related to the priors only 
    presents when \texttt{usePixelWeight} configuration is set to \texttt{False} during 
    the data reduction. 
    \song{
    Please see \citet{Bosch2017} (Section 4.4.9 and Appendix 2) for more details about
    the fitting algorithm of \cmodel{}.  
    In short, when \texttt{usePixelWeight} is set to \texttt{True}, \cmodel{} algorithm 
    will uses the per--pixel square root of the variance map for \texttt{coadd} image as 
    weights during the fitting.  
    When \texttt{usePixelWeight} is \texttt{False}, a constant weight will be used 
    instead.
    }  
    As one can see, this leads to significantly overestimated axis ratios for almost
    all galaxies\footnote{It also leads to underestimated half-light radius for the same
    galaxies.}.
    We repeat the \synpipe{} run for galaxies with 
    \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
    the problem. 
    When we use \texttt{usePixelWeight}$=$\texttt{True},
    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ provides an unbiased axis ratio 
    estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
    This change is still related to the bug in priors.  
    The actual effect of using per-pixel variance should be very small.  
    The next version of \hscpipe{} will fix this bug, and \synpipe{} will help evaluate 
    the precisions of shape and size measurements. 
    This is a good example that demonstrates how the \synpipe{} framework is valuable  
    for quality control and that can be used to improve \hscpipe{}.

    For the current HSC data release, we warn users against using the sizes and shapes 
    from \cmodel{} to study the structural properties of galaxies.
%% ------------------------------------------------------------------------------------ %%

@@

    \bibitem[Bosch et al.(2017)]{Bosch2017} Bosch, J., Armstrong, R., Bickerton, S., 
            et al.\ 2017, arXiv:1705.06766

@@

    %% O %%
    \bibitem[Oke(1974)]{Oke1974} Oke, J.~B.\ 1974, \apjs, 27, 21
